|

### 2021-03-23 01-Chp-Introduction.Rmd
End of day
Updates

## Aims and Objectives of the thesis

### Aim

### Objectives

   * To review the published literature with respect to the effec tof lipids and lipid regulating agents  
   * To examine whether there is evidence for an effect of lipid-regulating agents on dementia and related outcomes in a large scale population-based cohort, the Clinical Practice Research Datalink
   * To meta-analyze the

## Theoretical framework
The main theoretical framework used in this thesis is evidence synthesis - the discovery and critical integration of all available evidence on a research question in order to either: a) provide a more definitive answer to that question or; b) highlight gaps in the existing evidence base, so that future research address questions that have yet to be answered, or explores the same question in a way that increases our confidence in the result.

All elements of this thesis are based around this framework.

## Chapter Overview

* __Chapter \@ref(background-heading):__ Background information on dementia and blood lipid levels. This chapter provides an introduction to the topics covered in this thesis to non-subject area experts, and discusses the motivation for the remainder of the thesis. 
* __Chapter \@ref(sys-rev-tools-heading)__ This CHhapter introduces a new tool, the `medrxivr` R package, which was used to developed to allow for systematic searches of the bioRxiv and medRxiv preprint repositories.
* __Chapter \@ref(sys-rev-heading)__ This Chapter describes a comprehensive systematic review and meta-analysis of all available evidence on the relationship between blood lipids and lipid. 
* __Chapter \@ref(cprd-analysis-heading):__ This Chapter examines the relationship between lipid-regulating agent use and dementia outcomes in the Clinical Practice Research Datalink, a large primary care electronic health record database, based in England. 
* __Chapter \@ref(ipd-heading):__ This Chapter describes an individual patient data analysis of several longitudinal cohort studies, to describe the relationship between blood serum lipids and dementia outcomes.

## Thesis Output

@@

@@

  *

@@

## Summary

*
* 
*

>>>>

## Thesis Output {#thesis-output}

@@

  * McGuinness & Sheppard.

  * PRISMA papers and software

  * Discursive paper on open source in Evidence Synthesis

<!-- Essentially, look at the Trello   -->

@@

  * MSc Paper

@@

### 2021-03-23 02-Chp-Background.Rmd
Updates

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:dara-quote)', echo = TRUE}
Science knows it doesn't know everything; otherwise, it'd stop.
```
(ref:dara-quote) --- Dara O'Briain

# Background {#background-heading}
\minitoc <!-- this will include a mini table of contents-->

@@

Lay summaries appear at the beginning of each chapter, reviewed by the Patient and Public Involvement P

@@

> This chapter provides the context of the thesis. It briefly gives the background on the problem of increased adiposity, the biology of adipose tissue, and diseases linking increased body mass index and mortality. The chapter briefly explores different measures of increased adiposity and potential hypotheses for underlying aetiology of diseases associated with increased adiposity. Finally, the potential application of metabolites and Mendelian randomization in the context of understanding underlying aetiology are discussed. *From Matt Lee's thesis.*

@@

@@

### Definition and Subtypes
Dementia is major neurocognitive disorder, with symptoms including impairment of executive cognitive functions such as speech, judgement and memory. The most common causes of dementia are Alzheimer’s disease and vascular dementia, accounting for ~60-80% and ~10% of cases respectively. The remaining 10-30% of cases are caused other dementia subtypes (e.g. Lewy Body dementia) or by progression of other neurological diseases (e.g. Parkinson’s disease).

###	Diagnosis
Dementia is difficult to diagnose, primarily due to the absence of a gold standard test for the condition (is this true, or would it be better to say that there is no gold standard test without an autopsy). Information from multiple diagnostic tools are utilised, from medical history examination, through assessment of patients mental ability (e.g. the Mini-Mental State Examination), to clinical tests (e.g. Magnetic Resonance Imaging (MRI) scans).

@@

Several scales are commonly used to diagnose dementia and associated diseases for research purposes. Two of the most commonly used include the criteria of the Diagnostic and Statistical Manual of Mental Disorders, fourth edition (DSM-IV-TR)1 and the National Institute of Neurological Disorders and Stroke–Alzheimer Disease and Related Disorders (NINCDS–ADRDA).[@dubois2007] [**Need first NINCDS-ADRDA citation and DSM- **]

**Note important differences between the scales and whether they affect results. Could cross-reference with an exploratory analysis in Chapter \@ref(sys-rev-heading)**

###	Public Health Importance
Dementia is quickly becoming a critically important public health issue. Despite the age-specific incidence and prevalence of dementia remaining relatively constant over time,6 an ageing population looks set to create a dementia epidemic, particularly in Westernised countries. In the UK, there are estimated to be 800,000 people currently living with dementia, with this figure expected to double by 2040.7 Globally, the prevalence of dementia is expected to reach 75 million by 2030.8 Despite the number of dementia cases and decades of research, there remains much unknown about the pathogenesis and progression of the disease.

@@

### History
> Two major clinical trials are often cited as providing evidence that statins do not have an effect on the incidence ofdementia: the Prospective Study ofPravastatin in the Elderly (PROSPER) and the Medical Research
Council/British Heart Foundation Heart Protection Study; however, because of methodologic limitations in relation to dementia outcomes in these two trials, the results of these trials are difficult to evaluate. Dementia incidence or cognitive outcomes were not preplanned endpoints in either of them, neither study included a clinical cognitive evaluation, and numbers of patients with follow-up information for cognitive evaluations were not reported in either study manuscript. In PROSPER a post hoc analysis compared changes in cognitive scores over a 3-year period between statintreated and placebo patients and found no significant differences. In the MRC/BHF HPS trial,27
similar percentages of participants (0.3% in each—statin vs placebo—group) developed dementia during the 5-year follow-up period. The report did not state how the outcome of dementia was determined (e.g., reported as an adverse event or by follow-up phone interview).
*Taken from Cramer 2008 - included in review*

There exist only two large scale randomized controlled trials of the effect of statins on dementia risk - in fact these studies are the only two trials included in a 2016 review of statins for the prevention of dementia produced by the Cochrane [@mcguinness2016b]. Both showed no effect of

However, while being widely cited,

@@

@@

@@

``` {block type='correction'}
Measurement error is a big deal for this thesis, as will discuss measurement error regarding how  different codelists/measurement of AD vs vascular dementia affect results in later chapters.
```

@@

@@

## Methods used in the thesis

@@

he main theoretical framework used in this thesis is evidence synthesis - the identification, critical assessment, and integration of all available evidence on a research question in order to either: a) provide a more definitive answer to that question; or b) highlight gaps in the existing evidence base.

@@

### Primary cohort analysis

### Triangulation

### Individual patient data meta-analyis

## Summary

>>>>

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:dara-quote)', echo = TRUE}
Science knows it doesn't know everything; otherwise, it'd stop.
```

(ref:dara-quote) --- Dara O'Briain

# Background {#background-heading}

\minitoc <!-- this will include a mini table of contents-->

@@

@@

<!-- This chapter provides the context of the thesis. It briefly gives the background on the problem of increased adiposity, the biology of adipose tissue, and diseases linking increased body mass index and mortality. The chapter briefly explores different measures of increased adiposity and potential hypotheses for underlying aetiology of diseases associated with increased adiposity. Finally, the potential application of metabolites and Mendelian randomization in the context of understanding underlying aetiology are discussed. *From Matt Lee's thesis.* -->

@@

This Chapter will provide an overview of the thesis, introducing the core concepts used throughout and providing some background context on each. It will briefly discuss the natural history of dementia, it's public health importance and the .IN this context it will highlihg the importance of identifying easily modified treatment

It will also introduce the primary exp, covering their biological role, measurement and

Finally, it will outline the theoretical framework used in this thesis.

<!-- Dementia is a major neurocognitive disorder, the most common types of which are Alzheimer’s disease (AD) and vascular dementia (VaD) [1]. Much remains unknown about dementia pathogenesis, despite research implicating amyloid plaques and neurofibrillary tangles as potential mechanisms of disease [2]. Several cardiovascular elements have been identified as potential risk factors for dementia, and of these, lipid levels represent a promising target for preventative intervention due to the availability of lipid-modifying treatments. In this context, determining whether variations in lipid levels are causative for dementia may prove critical in reducing the future burden of the condition. -->

<!-- A role for lipids in the aetiology of dementia is supported by both genetic linkage studies and functional cell biology studies. The generation of the amyloid plaques found in the brains of Alzheimer’s patients is cholesterol dependent [3,4], while the most established genetic risk factor for late-onset dementia, apolipoprotein E (ApoE), is involved in cerebral cholesterol transport. Several other genes involved in cholesterol transport have also been found to be robustly associated with increased AD susceptibility [5-7].  -->

<!-- Despite these encouraging results, the evidence from epidemiological studies to date has been contradictory. Several observational studies have examined the relationships between concentrations of serum lipids (total cholesterol (TC), low density lipoprotein cholesterol (LDL-c), high density lipoprotein cholesterol (HDL-c) and triglycerides) and both Alzheimer’s disease and vascular dementia and reported widely different results. A high serum cholesterol concentration has been found to be associated with an increase in susceptibility to AD [8-13], though other studies have shown no association [14-17], or a reduced susceptibility [18,19]. With regards VaD, decreased levels of HDL-c appear to be associated with increased risk [18,20,21], while for LDL-c, studies have reported both positive and negative association [18,22].  -->

<!--  Observational studies do not represent the only source of evidence examining the link between lipid levels and dementia. A recent Cochrane review identified two large randomised controlled trials (RCTs) of statins for the prevention of dementia, indicating that assignment to late-life lipid modifying treatment, as a proxy for lower lipid levels, does not reduce dementia risk [23]. However, both RCTs were limited, primarily by the relatively short follow-up period examined, while one failed to report the criteria used to diagnose dementia [24,25]. Finally, as they included only patients at high vascular risk, their generalisability to other settings is limited [23].  -->

<!-- The use of newer methodological approaches, such as Mendelian randomisation (MR), has also produced contradictory results. In brief, MR uses genetic variants that are both strongly associated with the exposure of interest and are independent from potential confounders to strengthen causal inference [26]. A recent MR study indicated that low levels of LDL-c may cause a reduction in AD risk [27]. However, this study was criticised as it did not exclude the region surrounding the ApoE gene, meaning the risk reduction observed could be driven by variants in this region. -->

<!-- In short, each individual epidemiological approach taken to examine this research question is subject to distinct biases and short-comings that limit our ability to infer a causal relationship between blood lipids and subsequent dementia risk. However, as each approach will be subject to distinct biases, these differences in design can be advantageous. If all approaches point, or triangulate, towards the same answer, this strengthens the evidence of a causal link between lipid levels and dementia risk [26]. In this context, systematically identifying, assessing and integrating all available evidence in a triangulation framework, regardless of study design or approach taken, may help to increase our confidence that a causal relationship truly exists. -->

<!-- Finally, if lipids have a causal role in development of dementia, evidence-based preventative strategies would be informed by identifying the types of individuals who are most likely to receive benefit from treatment with lipid-modifying agents. Previous studies have hinted that the relationship is dependent on individual-level characteristics such as age and sex [16,28]. Meta-analyses of trial-level data often have limited ability to examine exposure-covariate interactions. An individual participant data (IPD) meta-analysis is therefore  -->

<!-- Consider sex as a biological variable -->

@@

### Definition and Subtypes

Dementia is major neurocognitive disorder, with symptoms including impairment of executive cognitive functions such as speech, judgement and memory. The most common causes of dementia are Alzheimer's disease and vascular dementia, accounting for ~60-80% and ~10% of cases respectively. The remaining 10-30% of cases are caused other dementia subtypes (e.g. Lewy Body dementia) or by progression of other neurological diseases (e.g. Parkinson's disease).

Two important considerations ont he

### Diagnosis

Dementia is difficult to diagnose, primarily due to the absence of a gold standard test for the condition. <!-- (is this true, or would it be better to say that there is no gold standard test without an autopsy?)--> Information from multiple diagnostic tools are utilised, from medical history examination, through assessment of patients mental ability (e.g. the Mini-Mental State Examination), to clinical tests (e.g. Magnetic Resonance Imaging (MRI) scans).

@@

Several scales are commonly used to diagnose dementia and associated diseases for research purposes. Two of the most commonly used include the criteria of the Diagnostic and Statistical Manual of Mental Disorders, fourth edition (DSM-IV-TR)1 and the National Institute of Neurological Disorders and Stroke--Alzheimer Disease and Related Disorders (NINCDS--ADRDA).[@dubois2007] [**Need first NINCDS-ADRDA citation and DSM-IV citations**

**Note important differences between the scales and whether they affect results. Could cross-reference with an exploratory analysis in Chapter** \@ref(sys-rev-heading)

### Public Health Importance

Dementia is quickly becoming a critically important public health issue. Despite the age-specific incidence and prevalence of dementia remaining relatively constant over time,6 an ageing population looks set to create a dementia epidemic, particularly in Westernised countries. In the UK, there are estimated to be 800,000 people currently living with dementia, with this figure expected to double by 2040.7 Globally, the prevalence of dementia is expected to reach 75 million by 2030.8 Despite the number of dementia cases and decades of research, there remains much unknown about the pathogenesis and progression of the disease.

@@

### History

> Two major clinical trials are often cited as providing evidence that statins do not have an effect on the incidence ofdementia: the Prospective Study ofPravastatin in the Elderly (PROSPER) and the Medical Research Council/British Heart Foundation Heart Protection Study; however, because of methodologic limitations in relation to dementia outcomes in these two trials, the results of these trials are difficult to evaluate. Dementia incidence or cognitive outcomes were not preplanned endpoints in either of them, neither study included a clinical cognitive evaluation, and numbers of patients with follow-up information for cognitive evaluations were not reported in either study manuscript. In PROSPER a post hoc analysis compared changes in cognitive scores over a 3-year period between statintreated and placebo patients and found no significant differences. In the MRC/BHF HPS trial,27 similar percentages of participants (0.3% in each---statin vs placebo---group) developed dementia during the 5-year follow-up period. The report did not state how the outcome of dementia was determined (e.g., reported as an adverse event or by follow-up phone interview). *Taken from Cramer 2008 - included in review*

There exist only two large scale randomized controlled trials of the effect of statins on dementia risk [CITE] - in fact these studies are the only two trials included in a 2016 review of statins for the prevention of dementia produced by the Cochrane [@mcguinness2016b]. Both showed no effect of

However, while being widely cited, these studies have major limitations that limiti their utility

in assessing the impact of lipid-lowering treatment on dementia risk.

@@

Risk factors for dementia

@@

At present fe

@@

```{block type='correction'}
Measurement error is a big deal for this thesis, as will discuss measurement error regarding how  different codelists/measurement of AD vs vascular dementia affect results in later chapters.
```

@@

Statins are the primary

<!----------------------------------------------------------------------------->

(ref:statin-mechanisam-cap) **Statin mechanism of action:**

(ref:statin-mechanisam-scap) Statin mechanism of action

```{r statin-mechanisam, echo = FALSE, results="asis", fig.cap='(ref:statin-mechanisam-cap)', out.width='100%', fig.scap='(ref:statin-mechanisam-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/prisma_flow.png"))
```

<!----------------------------------------------------------------------------->

@@

### Other lipid regulating agents (LRA)

## Theoretical framework

The main theoretical framework used in this thesis is evidence synthesis - the discovery and critical integration of all available evidence on a research question in order to either: a) provide a more definitive answer to that question or; b) highlight gaps in the existing evidence base, so that future research address questions that have yet to be answered, or explores the same question in a way that increases our confidence in the result.

All elements of this thesis are based around this framework.

@@

The main theoretical framework used in this thesis is evidence synthesis - the identification, critical assessment, and integration of all available evidence on a research question in order to either: a) provide a more definitive answer to that question; or b) highlight gaps in the existing evidence base.

@@

More specifically this includes the accurate searching of sources of grey literature (as enabled by the too presented in Chapter \@ref(sys-rev-tools-heading)) and risk of bias assessment.

### Involvement of patients and the public

Lay summaries appear at the beginning of each chapter, reviewed by the Patient and Public Involvement panel. They provide a plain language summary

## Chapter overview

* __Chapter \@ref(background-heading):__ Background information on dementia and blood lipid levels. This chapter provides an introduction to the topics covered in this thesis to non-subject area experts, and discusses the motivation for the remainder of the thesis. 
* __Chapter \@ref(sys-rev-tools-heading)__ This CHhapter introduces a new tool, the `medrxivr` R package, which was used to developed to allow for systematic searches of the bioRxiv and medRxiv preprint repositories.
* __Chapter \@ref(sys-rev-heading)__ This Chapter describes a comprehensive systematic review and meta-analysis of all available evidence on the relationship between blood lipids and lipid. 
* __Chapter \@ref(cprd-analysis-heading):__ This Chapter examines the relationship between lipid-regulating agent use and dementia outcomes in the Clinical Practice Research Datalink, a large primary care electronic health record database, based in England. 
* __Chapter \@ref(ipd-heading):__ This Chapter describes an individual patient data analysis of several longitudinal cohort studies, to describe the relationship between blood serum lipids and dementia outcomes.

## Aims and Objectives of the thesis

### Hypothesis

### Aim

### Objectives

-   To review the published literature with respect to the effec tof lipids and lipid regulating agents\
-   To examine whether there is evidence for an effect of lipid-regulating agents on dementia and related outcomes in a large scale population-based cohort, the Clinical Practice Research Datalink
-   To meta-analyze the

### 2021-03-23 03-Chp-Systematic-Review-Tools.Rmd
Updates

The tool has been well received by the community (as of `r date`, `medrxivr` has been downloaded more than `r medrxivr_downloads` times), and several use cases have been reported. It has been used to visualize the growing number of preprints related to the 2019 coronavirus outbreak [^chp-systematic-review-tools-3], perform searches of preprints as part of systematic reviews,[@noone2020] and examine how data-sharing behaviour is affected by different publication policies (preprint server versus journal).[CITE]

>>>>

The tool has been well received by the community (as of `r date`, `medrxivr` has been downloaded more than `r medrxivr_downloads` times), and several use cases have been reported. It has been used to visualize the growing number of preprints related to the 2019 coronavirus outbreak [^chp-systematic-review-tools-3], perform searches of preprints as part of systematic reviews,[@noone2020] and examine how data-sharing behaviour is affected by different publication policies (see \@ref(thesis-output)).[CITE]

### 2021-03-23 04-Chp-Systematic-Review.Rmd
Updates

```{block type='savequote', include=knitr::is_latex_output(),quote_author='(ref:sys-rev-quote)', echo = TRUE}
"It is surely a great criticism of our profession that we have not organised a critical summary by speciality or sub-speciality, up-dated periodically, of all relevant RCTS."  
```
(ref:sys-rev-quote) --- Archie Cochrane, 2000 [@cochrane20001931]

# Systematic review of all available evidence {#sys-rev-heading}
\minitoc <!-- this will include a mini table of contents-->

```{r, echo = FALSE, warning=FALSE, message=FALSE}
source("R/doc_options.R")
knitr::read_chunk("R/Chp2-Systematic-Review.R")
knitr::opts_chunk$set(echo = FALSE)
```

@@

* Examine how many times a primary study was included in a review  
* Look at whether searching preprints made any difference to my results
* Could apply ROBIS to previous reviews to see how they stack-up?

@@

* Evidence map - show the distribution of the different studies population across the world.
* Living systematic review approach - update weekly based on medRxiv

@@

The abstracts list of relevant conferences (e.g. the proceedings of the Alzheimer’s Association International Conference, published in the journal Alzheimer’s & Dementia) will be searched. Grey literature will also be searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, while theses will be accessed using the Open Access Theses and Dissertations portal. We will also search bioRxiv and medRxiv, preprint repositories using a tool built as part of this thesis, to identify potentially relevant studies. Finally, the reference lists of included studies will be searched by hand while studies citing included studies will be examined using Google Scholar (forward and reverse citation searching).

@@

#### Inclusion criteria
We will seek studies that examine the relationship between blood lipid levels (or any specific lipid fraction, including total cholesterol, HDL, LDL, and triglycerides) and risk of incident dementia/MCI. Eligible study designs include randomized controlled trials and non-randomized observational studies of lipid modifying treatments, longitudinal studies examining the effect of increased/decreased blood lipid levels, and genetic instrumental variable (Mendelian randomization) studies examining the effect of genetically increased/decreased blood lipid levels.

@@

Eligible studies will define dementia according to recognised criteria, for example the National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l’Enseignement en Neurosciences (NINDS-AIREN), International Classification of Diseases (ICD), or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria. For MCI, eligible studies are those that attempted state a definition for diagnoses of MCI (e.g. an adapted version of the Petersen criteria [@petersen1999]) and create ordinal groups of patients (e.g. no dementia or dementia/MCI/dementia) based on this definition.

@@

#### Exclusion criteria
Case-control studies, cross-sectional studies, qualitative studies, case reports/series and narrative reviews will be excluded. Studies which present no evidence of attempting to exclude prevalent cases from their analyses will also be excluded. Studies that measure change in continuous cognitive measures (e.g. MoCA score) without attempt to map these scores to ordinal groups (e.g. no dementia/MCI/dementia) will be excluded. Conference abstracts with no corresponding full-text publication will be examined, and we will contact authors to obtain information on the study’s status. Studies that are reported in insufficient detail (e.g. only in conference abstracts, new, letters, editorials and opinion) will be excluded. Previous systematic reviews will not be eligible, but their reference lists will be screened to identify any potentially relevant articles. Studies with outcomes not directly related to the clinical syndrome of dementia (e.g., neuroimaging), studies implementing a “multi-domain intervention” where the lipid-regulating agent is included in each arms (e.g. for example, a study examining exercise + statins vs statins alone, but a study examining exercise + statins vs exercise alone would be included), and studies where there was no screening for dementia at baseline except if the sample was initially assessed in mid-life (i.e. below the age of 50) will be excluded.

@@

@@

__Will need to include something in the methods section on this__

@@

*As part of our our forward snowballing exercise (where articles citing an included study are cited), we recorded whether a study included in our review had been included in any previous evidence synthesis attempt in an attempt to qualify the added value of this analysis. Additionally, if an included article was subsequently cited by a review, all studies in that review were screened for inclusion for the sake of completeness. This analysis was performed by extracting the citing articles from Google Scholar on XXXX and screening them manually. The DOI of articles extracted from this analysis are included in the appendix, as the Google Scholar search functionality is not readily reproducible.*

@@

<!----------------------------------------------------------------------------->
<!-- # ``` {r gwet-setup, results="hide", message=FALSE} -->
<!-- # ``` -->
<!-- # -->
<!-- # ```{r gwet-table, message=FALSE, results="asis"} -->
<!-- # ``` -->
<!----------------------------------------------------------------------------->

@@

-> Insert formula here. Need to be sure of how to calculate. [@gwet2008; @sim2005]

<!-- # ```{r agreementtableinter, echo = FALSE} -->
<!-- # ``` -->
<!-- # ```{r agreementtableintra, echo = FALSE} -->
<!-- # ``` -->

@@

<!----------------------------------------------------------------------------->
``` {r prisma-flow-setup, results="hide", message=FALSE}
```

(ref:prisma-flow-cap) __PRISMA Flowchart:__ Overview of how records moved through the systematic review process

@@

```{r prisma-flow-fig, echo = FALSE, results="asis", fig.cap='(ref:prisma-flow-cap)', out.width='100%', fig.scap='(ref:prisma-flow-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/prismaflow.png"))
```
<!----------------------------------------------------------------------------->

@@

<!----------------------------------------------------------------------------->
Include here:

* PRISMA Flowchart (use PRISMA2020 from GitHub - depending on level of involvement, could refer to the Appendix here too.)

* Summary of types of study

* Summary of locations

* Summary of diagnostic criteria used

* Summary of risk of bias

* Long table, horizontally. Newer version of flextable (GH) allows for PDF output

@@

* Check if there are protocols available for any of the published reports (unlikely for non-randomised controlled trials), and whether there were
* Vascular dementia has substantially less published reports. Many (reference Smeeth et al 2010 here) simply group into AD and non-AD making comparison between published st

@@

@@

* _Comprehensiveness:_ While several reviews of this research topic exist,[@chu2018b; @yang2020; @muangpaisan2010; @poly2020b] the overlap between the list of studies included in each is not 100%. As part of this review, I have not only performed a original search of primary literature databases, but have also screened the reference lists of comparable reviews to ensure no study has been omitted.
* _Structured risk of bias assessment:_ The majority of the highly cited reviews on this topic either do not formally consider the risk of bias in the observational studies they include or do not use an appropriate domain-based assessment tool (e.g. ROBINS-I/E). This is important area in which this thesis can add value, as based on the risk-of-bias assessments I have performed to date, several primary studies are at high risk of bias and this should be reflected in the findings of any  review on this topic.
* _Inclusion of preprints:_ Unlike other available reviews and enabled by the tool described in Chapter 3, this review systematically searched  preprinted health-related manuscripts as a source of grey literature. As part of this chapter, I plan to examine the extent of the additional information provided to the review by the inclusion of preprints.

@@

__The duplication of work across reviews (including, ironically, by this review) is substantial. In Section XXXX, I demonstrated that the each primary study included in this review was also included in other review so this topic, but that not all studies were included in all reviews. However, by creating a comprehensive review that attempted to draw together all available evidence from across the full range of study types.__

@@

>>>>

```{block type='savequote', include=knitr::is_latex_output(),quote_author='(ref:sys-rev-quote)', echo = TRUE}
"It is surely a great criticism of our profession that we have not organised a critical summary by speciality or sub-speciality, up-dated periodically, of all relevant RCTS."  
```

(ref:sys-rev-quote) --- Archie Cochrane, 2000 [@cochrane20001931]

# Systematic review of all available evidence {#sys-rev-heading}

\minitoc <!-- this will include a mini table of contents-->

```{r, echo = FALSE, warning=FALSE, message=FALSE}
source("R/doc_options.R")
knitr::read_chunk("R/Chp2-Systematic-Review.R")
```

@@

-   Examine how many times a primary study was included in a review\
-   Look at whether searching preprints made any difference to my results
-   Could apply ROBIS to previous reviews to see how they stack-up?

@@

-   Evidence map - show the distribution of the different studies population across the world.
-   Living systematic review approach - update weekly based on medRxiv

@@

The abstracts list of relevant conferences (e.g. the proceedings of the Alzheimer's Association International Conference, published in the journal Alzheimer's & Dementia) will be searched. Grey literature will also be searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, while theses will be accessed using the Open Access Theses and Dissertations portal. We will also search bioRxiv and medRxiv, preprint repositories using a tool built as part of this thesis, to identify potentially relevant studies. Finally, the reference lists of included studies will be searched by hand while studies citing included studies will be examined using Google Scholar (forward and reverse citation searching).

<!-- Include table with overview of search strategy here: summarise topics and how they were combined -->

The full search strategy for the Medline search, which was designed first and subsequently translated into the syntax for other databases is presented in Appendix \@ref(appendix-search-strategy).

@@

#### Inclusion criteria

We will seek studies that examine the relationship between blood lipid levels (or any specific lipid fraction, including total cholesterol, HDL, LDL, and triglycerides) and risk of incident dementia/MCI. Eligible study designs include randomized controlled trials and non-randomized observational studies of lipid modifying treatments, longitudinal studies examining the effect of increased/decreased blood lipid levels, and genetic instrumental variable (Mendelian randomization) studies examining the effect of genetically increased/decreased blood lipid levels.

@@

Eligible studies will define dementia according to recognised criteria, for example the National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN), International Classification of Diseases (ICD), or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria. For MCI, eligible studies are those that attempted state a definition for diagnoses of MCI (e.g. an adapted version of the Petersen criteria [@petersen1999]) and create ordinal groups of patients (e.g. no dementia or dementia/MCI/dementia) based on this definition.

@@

#### Exclusion criteria

Case-control studies, cross-sectional studies, qualitative studies, case reports/series and narrative reviews will be excluded. Studies which present no evidence of attempting to exclude prevalent cases from their analyses will also be excluded. Studies that measure change in continuous cognitive measures (e.g. MoCA score) without attempt to map these scores to ordinal groups (e.g. no dementia/MCI/dementia) will be excluded. Conference abstracts with no corresponding full-text publication will be examined, and we will contact authors to obtain information on the study's status. Studies that are reported in insufficient detail (e.g. only in conference abstracts, new, letters, editorials and opinion) will be excluded. Previous systematic reviews will not be eligible, but their reference lists will be screened to identify any potentially relevant articles. Studies with outcomes not directly related to the clinical syndrome of dementia (e.g., neuroimaging), studies implementing a "multi-domain intervention" where the lipid-regulating agent is included in each arms (e.g. for example, a study examining exercise + statins vs statins alone, but a study examining exercise + statins vs exercise alone would be included), and studies where there was no screening for dementia at baseline except if the sample was initially assessed in mid-life (i.e. below the age of 50) will be excluded.

@@

The risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation, as identified by a review of risk of bias assessments in systematic reviews of MR studies.[@mamluk2020]

A copy of the is available in Appendix \@ref(appendix-mr-rob). Advance results from this review were obtained from contact with the authors.

@@

**Will need to include something in the methods section on this**

@@

*As part of our our forward snowballing exercise (where articles citing an included study are cited), we recorded whether a study included in our review had been included in any previous evidence synthesis attempt in an attempt to qualify the added value of this analysis. Additionally, if an included article was subsequently cited by a review, all studies in that review were screened for inclusion for the sake of completeness. This analysis was performed by extracting the citing articles from Google Scholar on [DATE] and screening them manually. The DOI of articles extracted from this analysis are included in the appendix, as the Google Scholar search functionality is not readily reproducible.*

<!-- For the snowballing exercise - make sure you don't include studies published after review date: ~ June 2019 -->

@@

<!-- ------------------------------------------------------------------------- -->

```{r gwet-setup, results="hide", message=FALSE}
```

```{r gwet-table, message=FALSE, results="asis"}
```

<!-- ------------------------------------------------------------------------- -->

@@

-\> Insert formula here. Need to be sure of how to calculate. [@gwet2008; @sim2005]

<!-- # ```{r agreementtableinter, echo = FALSE} -->

<!-- # ``` -->

<!-- # ```{r agreementtableintra, echo = FALSE} -->

<!-- # ``` -->

@@

<!----------------------------------------------------------------------------->

```{r prisma-flow-setup, results="hide", message=FALSE}
```

(ref:prisma-flow-cap) **PRISMA Flowchart:** Overview of how records moved through the systematic review process

@@

```{r prisma-flow-fig, echo = FALSE, results="asis", fig.cap='(ref:prisma-flow-cap)', out.width='100%', fig.scap='(ref:prisma-flow-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/prismaflow.png"))
```

<!----------------------------------------------------------------------------->

@@

Include here:

-   PRISMA Flowchart (use PRISMA2020 from GitHub - depending on level of involvement, could refer to the Appendix here too.)

-   Summary of types of study

-   Summary of locations

-   Summary of diagnostic criteria used

-   Summary of risk of bias

-   Long table, horizontally. Newer version of flextable (GH) allows for PDF output

A common theme across the studies was a lack of data on vascular dementia. This is particularly interesting as lipids and statins are primarily a vascular disease. There is the potential that they studies encountered similar difficulties in address the unexpected results observed in the CPRD analysis in Chapter \@ref(cprd-analysis-heading). For vascular dementia, few studies exmined this outcome, primarily because of the absence (until recently) of

One item of particular interest in the absence of studies examining Mendelian randomisation studies is the absence of any effect following the adjustment for Apoe4. As covered in the discussion, ApoE4 genotype is the mjor risk factor for Alzheimer's disease.

In addition, there was quite a spread in terms fo the effect estimates used to th. Previous systematic review

### Converting risk ratios to odds ratios

Include formulae and informed assumptions

### Hazard ratios vs risk/odds ratios

Not interchangeable in the context of systematic review. If outcome is rare, odds and risk ratios approximate each other, but the hazard ratio is measuring something completely different, by taking into account time-to-event in each treatment group.

Several existing reviews do not distinguish between the two types of effect measures and include all existing studies in a single meta-analysis to produce an overall effect.

The likely effect of this is that the overall effect measures are biased towards . . . . ?

Can you predict the direction of effect from a

Best practice methods for dealing with disparate effect measures in included studies is to not perform a meta-analysis

<!-- See the third row of the table here; https://training.cochrane.org/handbook/current/chapter-12#section-12-1 -->

Some evidence of manipulation of effect estimates in previous reviews,(e.g. Chou, Sci Reports - at least one study disagrees with) but not documented in review text.

@@

-   Check if there are protocols available for any of the published reports (unlikely for non-randomised controlled trials), and whether there were
-   Vascular dementia has substantially less published reports. Many (reference Smeeth et al 2010 here) simply group into AD and non-AD making comparison between published st

@@

### Added evidental value of including preprints

<!-- Will to get actual numbers for this section -->

There were several relevant preprints captured by the search run using the tool presented in Chapter \@ref(sys-rev-tools-heading) (see Appendix \@ref(appendix-medrxivr-code)). While many of the preprints included were subsequently published by the time of submission of this thesis, at the time of the search they were only available

Of interest,

<!-- Triple check whether any of the studies have yet to be published -->

This likely reflects a bias in the type of study that is submitted, but indicates the additional evidential value of include preprints in the search strategy. It also means that searches are current - if the aim of systematic reviews is to

While the total number of relevant studies found using this method was

<!-- Can I explore the amount of information added by the preprints quantiatively using the weights in the meta-analysis -->

<!-- Add bit on comparison of preprints and published papers, demonstrating the preprints are a good reflection of -->

While these preprint have subsequently

@@

-   *Comprehensiveness:* While several reviews of this research topic exist,[@chu2018b; @yang2020; @muangpaisan2010; @poly2020b] the overlap between the list of studies included in each is not 100%. As part of this review, I have not only performed a original search of primary literature databases, but have also screened the reference lists of comparable reviews to ensure no study has been omitted.
-   *Structured risk of bias assessment:* The majority of the highly cited reviews on this topic either do not formally consider the risk of bias in the observational studies they include or do not use an appropriate domain-based assessment tool (e.g. ROBINS-I/E). This is important area in which this thesis can add value, as based on the risk-of-bias assessments I have performed to date, several primary studies are at high risk of bias and this should be reflected in the findings of any review on this topic.
-   *Inclusion of preprints:* Unlike other available reviews and enabled by the tool described in Chapter 3, this review systematically searched preprinted health-related manuscripts as a source of grey literature. As part of this chapter, I plan to examine the extent of the additional information provided to the review by the inclusion of preprints.

@@

**The duplication of work across reviews (including, ironically, by this review) is substantial. In Section XXXX, I demonstrated that the each primary study included in this review was also included in other review so this topic, but that not all studies were included in all reviews. However, by creating a comprehensive review that attempted to draw together all available evidence from across the full range of study types.**

<!-- Will hopefully be able to cite MSc review here to give details of other reviews -->

### Reviewing Mendelian randomisations studies

While

This may be because Mendelian randomisation studies have yet to reach a critical mass in terms of requiring a systematic review.

Recent updates, such as a guide to reading and interpreting. However, this guide includes reporting items in their quality checklist - reporting quality while important, is unrelated to internal validity.

Problems with overlapping samples in reviews of Mendelian randomisation studies in that we may be double counting participants - for

Methods for reviews of Mendelian randomisation studies are not well developed to account for the consideration above.

@@

Potentially missing other Mendelian randomisation studies, as we identified some through our snowball searching that were not captured by the search strategy. An example is Larsson et al. 2017[@larsson2017a], where the study examined the association between lipid fractions

Comment on the fact that several of the studies identified through the search of preprints, were subsequently published, but much later than the
